\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-15 proof-adaptive-optimality.tex
Rewrote entire proof of local asymptotic normality

\section{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
B(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

Lemma~\ref{lem:bound_intervals} is obtained as the special case $\delta = 0$ of lemma \ref{lem:bound_intervals_delta}. 
We now prove Lemma~\ref{lem:fisher_bound}.
\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
When $f(x)$ is the normal density function, this lemma follows from \cite[Thm. 3]{Barnes2018}. The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}. \\

The Fisher information of $B$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
\label{eq:lemma_J}
\end{align}
It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
\[
\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
\]
where the last transition is due to Assumption~1. 
\QEDA \\

We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
\begin{equation}
\label{eq:general_messages}
B_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \R$ is a Borel measurable set. 
%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
Consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of $(B_1,\ldots,B_n)$ given $\theta$. We have 
\begin{align}
P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f^2(0)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}.
\end{align*}
\QEDA

\subsection{Isoperimetric Lemma
\label{sec:bound_intervals_delta} }
The following lemma is used in the proof Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and \ref{thm:non_existence}.

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the function
\[
\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
\]
is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq  \max_{i} \eta_\delta(x_i).
\label{eq:lem_bound_intervals_delta}
\end{equation}
\end{lem}
In particular, 
\[
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
\]

\subsubsection*{
Proof of Lemma~\ref{lem:bound_intervals_delta}}
Denote 
\[
\delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
\]
\[
 \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
\]
where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
\begin{align}
\label{eq:lemm:interval_bounds:to_show}
\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
{\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
\end{align}
 Since 
\[
\eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
(1-\Delta_1(x)) \right|^{1+\delta}}, 
\]
The case $n=1$ is trivial.  
%follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that
\[
\eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
\]
Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
%For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
\begin{align}
& g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
&  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
\left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
} \label{eq:g_def}.
\end{align}
The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
\[
\max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
\]
where 
\[
A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
\right\}.
\]
Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
\[
c'(x) \triangleq \frac{f'(x)}{f(x)} 
\]
that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes

@@

where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.

@@

Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive. It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
\[
\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
\]

@@

Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 

@@

\[

@@

\]

@@

\]
\[

@@

\par  
In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
\[
c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
\]
Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function. Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection. It follows from the first part of the proof that, for any $\alpha>0$,
\begin{align}
\label{eq:proof:lem:bound_intervals}
\frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
\end{align}
where 
\[
\delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
\]
\[
\Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
\]
\[
\eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
\]
The proof is completed by noting that 
\lim_{\alpha \to 0} \frac{(\delta_{n,\alpha})^{2+\delta} }{ \left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}}  = \frac{(\delta_{n})^{2+\delta }}{\left(\Delta_{n}(1-\Delta_{n}) \right)^{1+\delta}},  
and, since the maximum is over a finite set,
\lim_{\alpha \to 0}  \max_i \eta_{\delta,\alpha}(x_i)  = \max_i\eta_\delta(x_i).

>>>>

\section{Proof of Theorem~\ref{thm:adpative_lower_bound}}
\label{proof:thm:adpative_lower_bound}

We begin with two technical lemmas.
\begin{lem} \label{lem:bound_intervals}
  Let $f$ be a log-concave and symmetric density function
  for which Assumption~\ref{assump:failure_rate} holds. For any $x_1 \geq
  \ldots \geq x_n \in \R$,
  \begin{equation}
    \frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }{
      \left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
    \leq  4f(0)^2.
    \label{eq:lem_bound_intervals}
  \end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
  Let $X$ be a random variable with a symmetric, log-concave, and
  continuously differentiable density function $f(x)$ such that Assumption~1
  holds. For a Borel measurable set $A$, define
  \begin{equation*}
    B(x) \defeq \begin{cases} 1
      & \mbox{if} ~x \in A, \\
      -1 & \mbox{if}~ x \notin A.
    \end{cases}
  \end{equation*}
  Then the Fisher information of $B$ with respect to $\theta$ is bounded
  from above by $\eta(0)$.
\end{lem}

Lemma~\ref{lem:bound_intervals} is the special case $\delta = 0$ of
Lemma~\ref{lem:bound_intervals_delta} to come in
Section~\ref{sec:bound_intervals_delta}.  We now prove
Lemma~\ref{lem:fisher_bound}.

\begin{proof-of-lemma}[\ref{lem:fisher_bound}]  
  When $f$ is the normal density function, this lemma follows from
  \cite[Thm.~3]{Barnes2018}. The proof below is based on a different techique
  than in \cite{Barnes2018}, and is valid for any log-concave symmetric
  density satisfying Assumption~\ref{assump:failure_rate}. \\

  The Fisher information of $B$ with respect to $\theta$ is given by
  \begin{align}
    I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
    & = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
    & =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
    & \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
    & = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
    & = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
  \end{align}
  where differentiation under the integral sign in $(a)$ is possible since
  $f$ is log-concave and so a.e.\ differentiable
  (cf.~\cite{Bertsekas73}),
  with a.e.\ derivative $f'(x)$. Regularity of
  the Lebesgue measure implies that for any $\epsilon>0$, there exists a
  finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
  \begin{equation*}
    \int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
  \end{equation*}
  which implies that for any $\epsilon' > 0$, the set $A$ in
  \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of
  disjoint intervals without increasing $I_\theta$ by more than
  $\epsilon'$. It is therefore enough to proceed in the proof assuming that
  $A$ is of the form
  \begin{equation*}
    A = \cup_{j=1}^k (a_j,b_j),
  \end{equation*}
  with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
  \begin{align*}
    \mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
    & = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
  \end{align*}
  so we may rewrite Eq.~\eqref{eq:lem_fisher_bound_proof1} as
  \begin{align*}
    I_\theta & =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
    { \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
    & \times \frac {1} 
    {1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
  \end{align*}
  It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in
  \R$ and any choice of the intervals' endpoints,
  \begin{equation*}
    I_\theta \le
    \max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f(t)^2 \leq 4 f(0)^2, 
  \end{equation*}
  where the last transition is by Assumption~\ref{assump:failure_rate}. 
\end{proof-of-lemma}

We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
To bound the Fisher information of any set of $n$ one-bit
messages with respect to $\theta$,
%% we first note that without loss of
%% each message $B_i$ can is of the form
%% \begin{equation}
%% B_i = \begin{cases}
%% X_i \in A_i & 1, \\
%% X_i \notin A_i & -1,
%% \end{cases} 
%% \end{equation}
%% where $A_i \subset \R$ is a Borel measurable set. 
%% %Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
we consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of
$(B_1,\ldots,B_n)$ given $\theta$. We have
\begin{align*}
  P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right),
  %% \label{eq:adpt_lower_bound_proof:1}
\end{align*}
where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1} \right) = \mathbb P\left(
X_i \in A_i\right)$, when $B_i = \indic{X_i \in A_i}$ by independence,
so that the Fisher information of $B_1,\ldots,B_n$ with
respect to $\theta$ is
\begin{align}
I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the
distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
Lemma~\ref{lem:fisher_bound} implies that $I_\theta
(B_i|B_{i-1},\ldots,B_1) \leq 4f(0)^2$. The Van Trees inequality
\cite{van2004detection, gill1995applications} now implies
\begin{align*}
\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}
\end{align*}
as desired.

\subsection{An Isoperimetric Lemma}
\label{sec:bound_intervals_delta}

The following lemma is essential to the the proofs
of Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and
\ref{thm:non_existence}.

\begin{lem}
  \label{lem:bound_intervals_delta}
  Let $f$ be a log-concave and symmetric density
  function. Let $\delta\geq 0$. Assume that the function
  \begin{equation*}
    \eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x)
    = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
  \end{equation*}
  is non-increasing in $|x|$. Then for any $x_1 \ge \ldots \ge x_n \in \R^n$,
  \begin{equation}
    \frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} } {\left|
      \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n
      (-1)^{i+1} F(x_i) \right|^{1+\delta} } \leq \max_{i} \eta_\delta(x_i).
    \label{eq:lem_bound_intervals_delta}
  \end{equation}
\end{lem}
In particular, 
\begin{equation*}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
\end{equation*}

\begin{proof-of-lemma}[\ref{lem:bound_intervals_delta}]
  Denote 
  \begin{equation*}
    \delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
  \end{equation*}
  \begin{equation*}
    \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
  \end{equation*}
  where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
  \begin{align}
    \label{eq:lemm:interval_bounds:to_show}
    \frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
         {\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
  \end{align}
  Since 
  \begin{equation*}
    \eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
      (1-\Delta_1(x)) \right|^{1+\delta}}, 
  \end{equation*}
  The case $n=1$ is trivial.  
  %follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
  Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that
  \begin{equation*}
    \eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
  \end{equation*}
  Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
  %For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
  Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
  \begin{align}
    & g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
    &  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
      \left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
    } \label{eq:g_def}.
  \end{align}
  The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
  \begin{equation*}
    \max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
  \end{equation*}
  where 
  \begin{equation*}
    A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
    \right\}.
  \end{equation*}
  %
  Since $f(x)$ is log-concave and symmetric, we may write $f(x) = e^{c(x)}$
  where $c(x)$ is concave, symmetric, and superdifferentiable on the interior
  of its domain with
  supergradient set $\partial c(x) = \{v \in \R \mid c(y) \le c(x) + v (y - x) ~
  \mbox{for~all}~ y\}$; $c$ is also
  differentiable a.e.\ with derivative
  \begin{equation*}
    c'(x) \triangleq \frac{f'(x)}{f(x)}
  \end{equation*}
  (when it exists), and we otherwise simply treat $f'(x) / f(x) = c'(x) \in
  \partial c(x)$ as an arbitrary element of the superdifferential.  The
  supergradient sets $\partial c(x)$ are increasing, in that $v_0 \in
  \partial c(x_0)$ and $v_1 \in \partial c(x_1)$ implies that $(v_1 - v_0)
  (x_1 - x_0) \le 0$.  We first prove the lemma under the assumption that
  $c$ is strictly concave, or, equivalently, that $v_i \in \partial c(x_i)$
  implies that $(v_1 - v_0)(x_1 - x_0) < 0$ whenever $x_1 \neq x_0$; that
  is, $c'$ is strictly decreasing.

  The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same
  $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes

@@

  where in the last display and henceforth we suppress the arguments
  $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and
  $\Delta_N$. (We may take the compactification of $\R$ as $[-\infty, \infty]$.)

@@

  Within the interior of $A_N(x^*,k)$, all three expressions in
  \eqref{eq:g_def} within an absolute value are positive. It follows that
  partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within
  the interior of $A_N(x^*,k)$ is
  \begin{equation*}
    \frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i
      f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N } +
    \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
  \end{equation*}

@@

  Since we assumed that $\partial c(x)$ is injective,
  equality~\eqref{eq:gradient_zero} holds if and only if $y_1 = \ldots
  = y_N$. In this case, $g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$ if $N$ is
  even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then

@@

  \begin{equation*}

@@

  \end{equation*}

@@

  \end{equation*}
  \begin{equation*}

@@

  In the case where $c(x)$ is not strictly concave, so that $c'$ does not
  strictly decrease, we approximate $c$ using another concave symmetric
  function with decreasing derivative. We assume w.l.o.g.\ that $c(0) = 0$
  maximizes $c$.  For $\alpha>0$ consider the function $f_\alpha(x) =
  \kappa(\alpha) e^{-|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ normalizes
  $f_\alpha$.  Then $c_\alpha(x)$ is concave, symmetric, and
  a.e.\ differentiable with
  \begin{equation*}
    c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
  \end{equation*}
  Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave
  function. Furthermore, since $c(x)$ is non-constant on any interval and
  $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval
  hence an injection. It follows from the first part of the proof that, for
  any $\alpha>0$,
  \begin{align}
    \label{eq:proof:lem:bound_intervals}
    \frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
  \end{align}
  where 
  \begin{equation*}
    \delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
  \end{equation*}
  \begin{equation*}
    \Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
  \end{equation*}
  and 
  \begin{equation*}
    \eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
  \end{equation*}
  The proof is completed by noting that 
  \begin{align*}
    \lim_{\alpha \to 0} \frac{(\delta_{n,\alpha})^{2+\delta} }{ \left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}}  = \frac{(\delta_{n})^{2+\delta }}{\left(\Delta_{n}(1-\Delta_{n}) \right)^{1+\delta}},  
  \end{align*}
  and, since the maximum is over a finite set,
  \begin{align*}
    \lim_{\alpha \to 0}  \max_i \eta_{\delta,\alpha}(x_i)  = \max_i\eta_\delta(x_i).
  \end{align*}
